Oriented Gradient Histogram applied to P300 Detection

### 2017-11-30 article.tex
Nueva ecuacion para la clasificacion

\noindent  where $ |J(\mathbf{x})| $ is the norm of the gradient vector found at each block of the patch, $\angle J(\mathbf{x}) $ is the angle of the gradient vector,  $\theta$ is the angle bin, $\mathbf{x}$ is a pixel from  the $i,j$-block $B_{i,j}$ and $ w_\mathrm{ang}(\cdot) $  and $ w_{ij}(\cdot) $ are linear interpolation functions used by Lowe and Vedaldi et al. in~\citep{Lowe2004,Vedaldi2010}.  Lastly, the fixed value of $ 3 $ is a magnification factor which corresponds to the number of pixels per each block when $s = 1$.  As the patch is of size $4 \times 4$ and  $8$ bin angles are considered, a descriptor of $128$ dimension is obtained. It can be observed that in each step, the histogram is computed by multiplying by $ |J(\mathbf{x})| $ , so the method considers both, the magnitude and the orientation of the gradient vector.

Fig.~\ref{fig:sampledescriptor} shows an example of a patch and a scheme of the histogram computation. Fig.~\ref{patch} is a plot of the signal and the patch centered in the keypoint. In Fig.~\ref{histogrambines} the possible orientations on each patch are illustrated. They form the corresponding $\mathbf{kp}$-descriptor of $128$ coordinates. The first two blocks orientations are shown.

@@

>>>>

\noindent  where $ |J(\mathbf{x})| $ is the norm of the gradient vector found at each block of the patch using finite differences, $\angle J(\mathbf{x}) $ is the angle of the gradient vector,  $\theta$ is the angle bin, $\mathbf{x}$ is a pixel from  the $i,j$-block $B_{i,j}$ and $ w_\mathrm{ang}(\cdot) $  and $ w_{ij}(\cdot) $ are linear interpolation functions used by Lowe and Vedaldi et al. in~\citep{Lowe2004,Vedaldi2010}.  Lastly, the fixed value of $ 3 $ is a magnification factor which corresponds to the number of pixels per each block when $s = 1$.  As the patch is of size $4 \times 4$ and  $8$ bin angles are considered, a descriptor of $128$ dimension is obtained. It can be observed that in each step, the histogram is computed by multiplying by $ |J(\mathbf{x})| $ , so the method considers both, the magnitude and the orientation of the gradient vector.

Fig.~\ref{fig:sampledescriptor} shows an example of a patch and a scheme of the histogram computation. Fig.~\ref{patch} is a plot of the signal and the patch centered in the keypoint. In Fig.~\ref{histogrambines} the possible orientations on each patch are illustrated. They form the corresponding $\mathbf{kp}$-descriptor of $128$ coordinates. The first two blocks orientations are shown.  Following this procedure for every assigned keypoint, we obtain $N_{kp}$ descriptors.

@@

The aim is to identify the selected letter from the matrix. Previously, during training phase, descriptors from labeled segments are extracted.  The P300 templates are grouped in a template set called $ T $.  Rows are labeled 1-6, whereas columns are labeled 7-12.  The process has the following steps:

\begin{enumerate}
\item Highlight randomly the rows and columns from the matrix.  There are one row and one column that matches the selected letter by the user.
\item For $ k= {1-6} $: Obtain the descriptor from the image of the signal plot according to the method described in Section~\ref{Feature}, $ d^r_1, \dots  d^r_6 $ for rows and  $ d^c_1, \dots  d^c_6 $ 
\item For $ k= {7-12} $: Compute

\begin{equation}
\hat{r} = \arg \min_u \sum_{q \in NN_T(d^r_u)}^{} \left\lVert q -  d^r_u \right\rVert ^2,\; u = 1,\dots,6
\label{eq:multiclassification}
\end{equation}

\noindent This procedure is repeated for the 6 columns.

\begin{equation}
\hat{c} = \arg \min_u \sum_{q \in NN_T(d^c_u)}^{} \left\lVert q -  d^c_u \right\rVert ^2,\; u = 7,\dots,12
\label{eq:multiclassification}
\end{equation}

\end{enumerate}
